---
title: "LoxCode"
output: 
  flexdashboard::flex_dashboard:
    theme: yeti
    orientation: rows
    vertical_layout: scroll
    
params:
  format: NA
  functions: NA
  types: NA
  inputs: NA
  annotations: NA
  loxcodes: NA
---


<style>
.chart-shim{
 overflow-x:auto;
 overflow-y:auto;
}


.navbar {
  background-color:rgb(255,0,0,0.8);
  border-color:grey;
}

.navbar-inverse .navbar-nav > li > a:hover,
.navbar-inverse .navbar-nav > li > a:focus {
    background-color: white;
    color: black;
}

.navbar-inverse .navbar-nav > .active > a,
.navbar-inverse .navbar-nav > .active > a:hover,
.navbar-inverse .navbar-nav > .active > a:focus {
  color: white;
  background-color: grey;
}

.navbar-brand {
color:white!important;
font-size:30px!important;
}
</style>  


### **LoxCodeR** 


Summary
=====================================


Row {data-width=150}
--------------------

```{r setup, include=FALSE}
library(tidyverse)
library(crosstalk)
library(ggplot2)
library(ggthemes)
library(reshape2)
library(DT)
library(leaflet)
library(scatterD3)
library(highcharter)
library(flexdashboard)

eval = TRUE
links = TRUE 
```

```{r}
# nPlot = length(params$functions)
# if (count == 0) { eval = FALSE }
```

### Data

```{r}
l1=list()
for (i in 1:length(names(params$inputs[[1]][[1]]@samples))){
  l1=append(l1,params$inputs[[1]][[1]]@samples[[i]]@decode_stats$tot_reads)
}
count=0
for (i in unlist(l1,recursive=F)){
  if (i<5000){count=count+1}
}
col = c("Samples","barcodes","average reads/sample","less than 5000 read", "complexity warning",length(unique(params$inputs[[1]][[1]]@samp_table$sample)),0,mean(unlist(l1,recursive=F)),count,0)
m=matrix(col,ncol=2,byrow = F)
DT::datatable(m, options = list(
  bPaginate = FALSE,
  dom = 't'
))
#params$inputs[[1]][[1]]@samp_table
```


<!-- ### Bar Code {data-width=60} -->

<!-- ```{r} -->
<!-- bar_code <- 45 -->
<!-- valueBox(bar_code, icon = "ion-erlenmeyer-flask") -->
<!-- ``` -->

<!-- ### Comments {data-width=60} -->

<!-- ```{r} -->
<!-- comments <- 10000 -->
<!-- valueBox(comments, -->
<!--          color = "rgb(0,128,128)", -->
<!--          icon = "fa-comments") -->
<!-- ``` -->

<!-- ### xxx {data-width=60} -->

<!-- ```{r} -->
<!-- xxx <- 8888 -->
<!-- valueBox(xxx, -->
<!--          icon = "ion-android-checkbox-outline", -->
<!--          color = ifelse(xxx > 10, "warning", "primary")) -->
<!-- ``` -->



Row {.tabset .tabset-fade}
-------------------------------------
### Experiment 1
```{r echo=FALSE}

paramsAsText <- function(params) {
  parametersAsText = list()
  for (i in 1:length(params)) {
    n = names(params)[[i]]
    p = params[[i]]
    if (is(p, "loxcode_experiment") | is(p, "loxcode_sample")) {
      parametersAsText = list.append(parametersAsText, paste(n, "=", p@name))
    }
    else if (is.character(p)) {
      parametersAsText = list.append(parametersAsText, paste(n, "=", p))
    }
    else if (is.numeric(p)) {
      parametersAsText = list.append(parametersAsText, paste(n, "=", paste(p, ",")))
    }
    else if (rapportools::is.boolean(p)) {
      parametersAsText = list.append(parametersAsText, paste(n, "=", p))
    }
  }
  return(paste(parametersAsText, collapse=", "))
}

```

```{r}
plotTitle <- function(ptype){
  if(ptype == "size_plot"){
    cat("###", "Size Plot",  "  \n")
  } else if (ptype == "complexity_plot"){
    cat("###", "Complexity Plot",  "  \n")
  } else if (ptype == "ratio_plot"){
    cat("###", "Ratio Plot",  "  \n")
  } else if (ptype == "both_plot"){
    cat("###", "Both Plot",  "  \n")
  } else if (ptype == "sample_size_plot"){
    cat("###", "Sample Size Plot",  "  \n")
  } else if (ptype == "sample_complexity_plot"){
    cat("###", "Sample Complexity Plot",  "  \n")
  } else if (ptype == "heatmap_plot"){
    cat("###", "Heatmap Plot",  "  \n")
  } else if (ptype == "bubble_plot"){
    cat("###", "Bubble Plot",  "  \n")
  } else if (ptype == "saturation_plot"){
    cat("###", "Saturation Plot",  "  \n")
  } else if (ptype == "pair_comparison_plot"){
    cat("###", "Pair Comparison Plot",  "  \n")
  }else{
    cat("###", "Plot",  "  \n")
  }
}

```





```{r results='asis'}
plt <- htmltools::tagList()
#params
j=1
for (i in c(1,2,5,6,7)){
if(params$types[[i]]=='ratio_plot' || params$types[[i]]=='both_plot'){
g <- do.call(params$functions[[i]], params$inputs[[i]])
plt[[j]]=ggplotly(g,height = 6000) 
j=j+1
plt[[j]]=params$annotations[[i]]
j=j+1 }else if(params$types[[i]]=='sample_complexity'){
  g <- do.call(params$functions[[i]], params$inputs[[i]])
plt[[j]]=ggplotly(g) 
j=j+1
plt[[j]]=params$annotations[[i]]
j=j+1 }else{
 g <- do.call(params$functions[[i]], params$inputs[[i]])
plt[[j]]=ggplotly(g) 
j=j+1
plt[[j]]=params$annotations[[i]]
j=j+1
#params$inputs[[i]]
cat('\n')
}
}
```

```{r results='asis',autodep=TRUE}
plt
```



```{r results='asis',autodep=TRUE}
plt <- htmltools::tagList()
list1=c()
j=1
#params
if (length(params$types)>5){
for (i in 8:length(params$types)){
  if (!(params$inputs[[i]][[2]] %in% list1)){
    list1=c(list1,params$inputs[[i]][[2]])
    #cat(paste("### text"))
  }
}
for (i in 8:length(params$types)){
  if(length(list1)>0){
  if (params$inputs[[i]][[2]]==list1[1]){
if(params$types[[i]]=='ratio_plot' || params$types[[i]]=='both_plot'){
g <- do.call(params$functions[[i]], params$inputs[[i]])
plt[[j]]=ggplotly(g,height = 6000) 
j=j+1
plt[[j]]=params$annotations[[i]]
j=j+1 }else if(params$types[[i]]=='sample_complexity'){
  g <- do.call(params$functions[[i]], params$inputs[[i]])
plt[[j]]=ggplotly(g)
j=j+1
plt[[j]]=params$annotations[[i]]
j=j+1 }else{
 g <- do.call(params$functions[[i]], params$inputs[[i]])
plt[[j]]=ggplotly(g) 
j=j+1
plt[[j]]=params$annotations[[i]]
j=j+1
#params$inputs[[i]]

cat('\n')
}
}
}
  }
  if(length(list1)<2){list1=c()}
   else{list1=list1[2:length(list1)]}
}
```

```{r results='asis',autodep=TRUE}
plt
```


```{r child = '/home/arnav/Desktop/LoxCodeR2024/LoxcodeR_app/chapter1.Rmd'}
```



Sample Comparision
=====================================
Row {.tabset .tabset-fade}
-------------------------------------
### Ratio Plot
```{r results='asis',autodep=TRUE}
ggplotly(do.call(params$functions[[3]], params$inputs[[3]]),height = 200*length(params$inputs[[3]][[1]]@count_matrixes[[length(params$inputs[[3]][[1]]@count_matrixes)]]/4))
```

### Both Plot
```{r results='asis',autodep=TRUE}
ggplotly(do.call(params$functions[[4]], params$inputs[[4]]),height = 200*length(params$inputs[[4]][[1]]@count_matrixes[[length(params$inputs[[4]][[1]]@count_matrixes)]]/4))
```
Experiment Data
=====================================


Row {.tabset .tabset-fade}
-------------------------------------

### Samples

```{r }
library(DT)

#print(params$inputs[[1]][[1]]@samp_table) , scrollY = "1000px", , options = list(pageLength = 5)

datatable(params$inputs[[1]][[1]]@samp_table, options = list(pageLength = 5, scrollY = "2000px"))


#datatable(co2sorted, options = list(pageLength = 6))
```


### Code set

```{r }

#print(params$inputs[[1]][[1]]@samp_table) , options = list(pageLength = 5), scrollY = "1000px"

datatable(params$inputs[[1]][[1]]@code_sets[["all_codes"]], options = list(pageLength = 5, scrollY = "2000px"))


#datatable(co2sorted, options = list(pageLength = 6))
```


```{r child = '/home/arnav/Desktop/LoxCodeR2024/LoxcodeR_app/chapter4.Rmd'}
```



```{r child = '/home/arnav/Desktop/LoxCodeR2024/LoxcodeR_app/chapter3.Rmd'}
```



Details
=====================================

```{r child = '/home/arnav/Desktop/LoxCodeR2024/LoxcodeR_app/chapter5.Rmd'}
```
